---
title: "Public Sphere Sentiment Following a School Shooting"
output: html_document
classoption: landscape
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE) #, fig.width = 8, fig.height = 6)
```

```{r }
library(dplyr)
library(ggplot2)
library(reshape2)

load(file = 'summaries.rda')
sentiment_grouped <- group_by(for_shiny, event, source.type)
sentiment_grouped$date.event <- c( '2006-10-02', '1999-04-20', 
                                   '2012-12-14', '2012-12-14', 
                                   '2015-10-01', '2015-10-01', 
                                   '2007-04-16', '2007-04-16')
sentiment_grouped$date.event <- as.Date(sentiment_grouped$date.event)

avg_sentiment <- summarise(sentiment_grouped,
                           anger = anger,
                           disgust = disgust,
                           fear =  fear,
                           sadness = sadness,
                           surprise = surprise)%>% melt
names(avg_sentiment) <- c('event', 'source', 'sentiment', 'score')
vt_sentiment <- subset(avg_sentiment, event == 'VT')
ucc_sentiment <- subset(avg_sentiment, event == 'UCC')
sh_sentiment <- subset(avg_sentiment, event == 'SH')
ami_sentiment <- subset(avg_sentiment, event == 'AMI')
chs_sentiment <- subset(avg_sentiment, event == 'CHS')

```

###Time
```{r time, echo = FALSE, fig.width = 4, fig.height = 3}
par(mfrow = c(2,3))
qplot(sentiment_grouped$date.event, sentiment_grouped$surprise, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Surprise", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")
# qplot(sentiment_grouped$date.event, sentiment_grouped$negative, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Overall Negative Sentiment", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")
qplot(sentiment_grouped$date.event, sentiment_grouped$anger, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Anger", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")
qplot(sentiment_grouped$date.event, sentiment_grouped$fear, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Fear", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")
qplot(sentiment_grouped$date.event, sentiment_grouped$disgust, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Disgust", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")
qplot(sentiment_grouped$date.event, sentiment_grouped$sadness, ylim = c(0, 0.2), ylab = "mean adjusted score", xlab = "year", main = "Sadness", colour = sentiment_grouped$source.type) + geom_line() + labs(colour = "source")

```

## Responsiveness 30-days after
```{r}
load(file = 'all_messages.rda')

twitter_sandy_hook <- filter(all_messages, event == 'SH', source == 'twitter')
twitter_virginia_tech <- filter(all_messages, event == 'VT', source == 'twitter')
twitter_umpqua <- filter(all_messages, event == 'UCC', source == 'twitter')



vt_tweets.by_date <- twitter_virginia_tech %>% group_by(date) %>% summarise(total = n())
#qplot(vt_tweets.by_date$date, vt_tweets.by_date$total)
vt_tweets.by_date$proportion <- vt_tweets.by_date$total/5000
#qplot(vt_tweets.by_date$date, vt_tweets.by_date$proportion)

sh_tweets.by_date <- twitter_sandy_hook %>% group_by(date) %>% summarise(total = n())
#qplot(sh_tweets.by_date$date, sh_tweets.by_date$total)
sh_tweets.by_date$proportion <- sh_tweets.by_date$total/400000000
#qplot(sh_tweets.by_date$date, sh_tweets.by_date$proportion)

ucc_tweets.by_date <- twitter_umpqua %>% group_by(date) %>% summarise(total = n())
#qplot(ucc_tweets.by_date$date, ucc_tweets.by_date$total)
ucc_tweets.by_date$proportion <- ucc_tweets.by_date$total/500000000
#qplot(ucc_tweets.by_date$date, ucc_tweets.by_date$proportion)

vt_tweets.by_date$days.from.event <- vt_tweets.by_date$date - as.Date('2007-04-16')
sh_tweets.by_date$days.from.event <- sh_tweets.by_date$date - as.Date('2012-12-14')
ucc_tweets.by_date$days.from.event <- ucc_tweets.by_date$date - as.Date('2015-10-01')


ucc_tweets.by_date$event <- 'Umpqua Community College'
sh_tweets.by_date$event <- 'Sandy Hook Elementary'
vt_tweets.by_date$event <- 'Virginia Tech'

tweets_by_date <- rbind(ucc_tweets.by_date, sh_tweets.by_date)
tweets_by_date <- rbind(tweets_by_date, vt_tweets.by_date)
tweets_by_date$days.from.event <- as.integer(tweets_by_date$days.from.event)

ggplot(tweets_by_date, aes(days.from.event, total)) +
       geom_line(aes(colour = event))  
  
ggplot(tweets_by_date, aes(days.from.event, proportion)) +
       geom_line(aes(colour = event))  


# 5000; 400,000,000; 500,000,000

```



```{r}


```{r }
#par(mfrow = c(2,2))
load("avg_sentiment.rda")
load("all_sentiment.rda")

avg_letter_sentiment <- subset(avg_sentiment, source == 'Letter')
avg_twitter_sentiment <- subset(avg_sentiment, source == 'Twitter')

qplot(event_order, score, data = all_sentiment, 
      color = sentiment, geom = "line") +
    ggtitle("Tweets & Letters") + xlab("") +
    scale_x_discrete(limits = c("Columbine", "Amish School",
                                "Virginia Tech", "Sandy Hook",
                                "Umpqua"))

qplot(event_order, score, data = avg_letter_sentiment, 
      color = sentiment, geom = "line") + 
    ggtitle("Letters") + xlab("") +
    scale_x_discrete(limits = c("Columbine", "Amish School",
                                "Virginia Tech", "Sandy Hook",
                                "Umpqua"))
    
qplot(event_order, score, data = avg_twitter_sentiment, 
      color = sentiment, geom = "line") + 
    ggtitle("Twitter") + xlab("") +
    scale_x_discrete(limits = c("Columbine", "Amish School",
                                "Virginia Tech", "Sandy Hook",
                                "Umpqua"))  



#anger
letter_anger <- subset(avg_letter_sentiment, sentiment == 'anger')
twitter_anger <- subset(avg_twitter_sentiment, sentiment == 'anger')
# plot(letter_anger$event_order, letter_anger$score)
# plot(twitter_anger$event_order, twitter_anger$score)

#sadness
letter_sadness <- subset(avg_letter_sentiment, sentiment == 'sadness')
twitter_sadness <- subset(avg_twitter_sentiment, sentiment == 'sadness')
# plot(letter_sadness$event_order, letter_sadness$score)
# plot(twitter_sadness$event_order, twitter_sadness$score)

#fear
letter_fear <- subset(avg_letter_sentiment, sentiment == 'fear')
twitter_fear <- subset(avg_twitter_sentiment, sentiment == 'fear')
# plot(letter_fear$event_order, letter_fear$score)
# plot(twitter_fear$event_order, twitter_fear$score)

#disgust
letter_disgust <- subset(avg_letter_sentiment, sentiment == 'disgust')
twitter_disgust <- subset(avg_twitter_sentiment, sentiment == 'disgust')
# plot(letter_disgust$event_order, letter_disgust$score)
# plot(twitter_disgust$event_order, twitter_disgust$score)

#surprise
letter_surprise <- subset(avg_letter_sentiment, sentiment == 'surprise')
twitter_surprise <- subset(avg_twitter_sentiment, sentiment == 'surprise')
# plot(letter_surprise$event_order, letter_surprise$score)
# plot(twitter_surprise$event_order, twitter_surprise$score)



```

